---
title: "01-rmd-example"
author: "Nicholas Tierney"
date: 2017/06/27
output: html_document
---

# Tasks

- Make a report with an introduction heading
- Add your name and date to the YAML header

Describe the data from the airquality dataset using blockquotes (hint: `?airquality`, it is built into R.)

Today we are going to be looking at the dataset, `airquality`.
This dataset contains information on:

This is a quote:

> Daily air quality measurements in New York, May to September 1973.

Ther variables in the dataset contain:

- Ozone	numeric	Ozone (ppb)
- Solar.R	numeric	Solar R (lang)
- Wind	numeric	Wind (mph)
- Temp	numeric	Temperature (degrees F)
- Month	numeric	Month (1--12)
- Day	numeric	Day of month (1--31)


- Make a library call in the code chunk
```{r}

"this is code"

library(tidyverse)

```

```{r}
plot(airquality$Ozone,
     airquality$Solar.R)
```
OR you can use ggplot

```{r}
library(ggplot2)

ggplot(airquality,
       aes(x = Ozone,
           y = Solar.R)) + 
  geom_point()
```


- Make a plot of ozone and solar radiation

Extra: 

- Make a plot of ozone and temperature

